---
title: "Option 1: Traditional Website"
output: 
    html_document:
        toc: TRUE
        toc_float: TRUE
editor_options: 
  chunk_output_type: console
---

<br>

# To do if using this website

* Rerender the html reports using the css style sheet in the root directory of this website so that the top banner is included and “Home” can be seen

* Alternatively, rerender the html reports with an embedded link to "Home" at the top

* Clean up the html reports
  * Better titles 
  * Remove the generic pieces (keep only pieces specific to a given site)
  * Use `formattable` to make nicer looking tables
  * Add some figures

<br>

```{r}

library(fs)
library(here)
surv.dir = path(here::here("InitalDataCleaning/Survey\ report/Scantron\ data/Cleaning\ Report\ 12072021/SurveyOnly\ cleaning\ report."))

```


# Detailed site reports

## [Test](`r path(paste0(surv.dir, "Los\ Angeles\ County.80.html"))`)
<!---
## [Los Angeles County - 80](InitalDataCleaning/Survey\ report/Scantron\ data/Cleaning\ Report\ 12072021/SurveyOnly\ cleaning\ report.Los\ Angeles\ County.80.html)

## [Northern CA - 30](InitalDataCleaning/Survey\ report/Scantron\ data/Cleaning\ Report\ 12072021/SurveyOnly\ cleaning\ report.Northern CA.30.html)

## [Greater CA - 10](InitalDataCleaning/Survey\ report/Scantron\ data/Cleaning\ Report\ 12072021/SurveyOnly\ cleaning\ report.Greater CA.10.html)

## [Detroit - 60](InitalDataCleaning/Survey\ report/Scantron\ data/Cleaning\ Report\ 12072021/SurveyOnly\ cleaning\ report.Detroit.60.html)

## [Louisiana - 40](InitalDataCleaning/Survey\ report/Scantron\ data/Cleaning\ Report\ 12072021/SurveyOnly\ cleaning\ report.Louisiana.40.html)

## [Georgia - 20](InitalDataCleaning/Survey\ report/Scantron\ data/Cleaning\ Report\ 12072021/SurveyOnly\ cleaning\ report.Georgia.20.html)

## [Michigan - 61](InitalDataCleaning/Survey\ report/Scantron\ data/Cleaning\ Report\ 12072021/SurveyOnly\ cleaning\ report.Michigan.61.html)

## [New Jersey - 50](InitalDataCleaning/Survey\ report/Scantron\ data/Cleaning\ Report\ 12072021/SurveyOnly\ cleaning\ report.New Jersey.50.html)

## [Texas - 70](InitalDataCleaning/Survey\ report/Scantron\ data/Cleaning\ Report\ 12072021/SurveyOnly\ cleaning\ report.Texas.70.html)

## [WebRecruit - 99](InitalDataCleaning/Survey\ report/Scantron\ data/Cleaning\ Report\ 12072021/SurveyOnly\ cleaning\ report.WebRecruit.99.html)

## [USC Other - 81](InitalDataCleaning/Survey\ report/Scantron\ data/Cleaning\ Report\ 12072021/SurveyOnly\ cleaning\ report.USC Other.81.html)

## [USC MEC - 82](InitalDataCleaning/Survey\ report/Scantron\ data/Cleaning\ Report\ 12072021/SurveyOnly\ cleaning\ report.USC MEC.82.html)
--->
<br>

# Some nice interactive visual

Add something helpful here, maybe a map of all sites?

<br>

<br>

```{r setup, message=FALSE, echo=FALSE, warning=FALSE}

library(data.table)
library(tidyverse)
library(dplyr)
library(plotly)
library(DT)
library(knitr)
library(here)
library(fs)

# Initialize code chunk options
opts_chunk$set(
  warning = FALSE,
  message = FALSE,
  eval=TRUE,
  echo = TRUE,
  cache = FALSE,
  fig.width = 7, 
  fig.align = 'center',
  fig.asp = 0.618,
  out.width = "700px",
  class.source = "code-r")
```


<br>
<br>