---
title: "Summary Report for the Merged Registry and Survey Data"
author: "RESPOND Core D Team"
date: "`r format(Sys.time(), '%Y-%m-%d')`"
output:
  html_document:
    toc: true
    toc_float: true
    df_print: paged
    code_folding: hide
  pdf_document: default
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
require("RPostgreSQL") # for PostgreSQL
library(zoo) # for date conversion
library(expss) # for labels
library(DBI) # for Database connectivity
library(summarytools) # for summarizing variables
library(tidyverse)
library(plyr)
library(knitr) # for creating tables
#library(questionr)
library(table1)
library(xtable)
library(ggplot2)
#library(epiDisplay)
library(memisc)

knitr::opts_chunk$set(warning = FALSE)

```

```{r input data} 
# set working directory
setwd("/Volumes/GoogleDrive/My Drive/Projects/RESPOND/CORE D/DataProcessingCleaningCreation/MergeData")
available_data_files <- list.files("../Data/")
load(paste("../Data/", sort(available_data_files[grep("vmerged_", available_data_files)], decreasing = T)[1], sep=""))

```

# Description

This report is merges the registry data and the survey data in the RESPOND study.

### Total Number of Individuals: `r nrow(d)`

# REGISTRY	
```{r registry }  
registry_count <- d %>% 
  group_by(registry) %>% 
  dplyr::summarise(n = n())
kable(registry_count, format = "simple", align = 'l', caption = "Overview of all registries")
```


# RESPOND ID
* From Barcode label put on last page of survey by registries, identifies participant. RESPOND_ID is assigned by the registries.
```{r respond id, echo=FALSE}
d_respondid <- filter(d, !is.na(respondid))

isDup_respondid <- duplicated(d_respondid$respondid)
numDups_respondid <- sum(isDup_respondid)
dups_respondid <- d_respondid[isDup_respondid, 'respondid']

```

    + Number of duplicates: `r numDups_respondid`

    + Number of NAs: `r sum(is.na(d$respondid))`


# SURVEY ID
- Scantron assigned SurveyID
```{r survey ID, echo=FALSE}
isDup_surveyid <- duplicated(d$surveyid)
numDups_surveyid <- sum(isDup_surveyid)
dups_surveyid <- d[isDup_surveyid, 'surveyid']

```


    + Number of duplicates: `r numDups_surveyid`
    + The following are duplicated IDs:
    + `r dups_surveyid`


    + Number of NAs: `r sum(is.na(d$surveyid))`


# Summary Tables

```{r p_value function for tables, echo=FALSE}
pvalue <- function(x, ...) {
    # Construct vectors of data y, and groups (strata) g
    y <- unlist(x)
    g <- factor(rep(1:length(x), times=sapply(x, length)))
    if (is.numeric(y)) {
        # For numeric variables, perform a anova ## standard 2-sample t-test
        p <- anova(lm(y~g))$`Pr(>F)`   # t.test(y ~ g)$p.value  
    } else {
        # For categorical variables, perform a chi-squared test of independence
        p <- chisq.test(table(y, g))$p.value
    }
    # Format the p-value, using an HTML entity for the less-than sign.
    # The initial empty string places the output on the line below the variable label.
    c("", sub("<", "&lt;", format.pval(p, digits=3, eps=0.001)))
}

```


## Aggressiveness ('grant') 
### By Cancer History
```{r agg_grant by cancers, results='asis'}
table1(~ Breast_Yes+Ovarian_Yes+Colorectal_Yes+Lung_Yes+Other_Cancer_Yes+Any_Cancer_Yes | aggressiveness_grant, extra.col=list('P-value'=pvalue), data=d, topclass="Rtable1-shade", overall=FALSE)

```

### By Comorbidities
```{r agg_grant by comorbidities, results='asis'}

table1::label(d$b4aa) <- "Heart_Attack"
table1::label(d$b4ba) <- "Heart_Failure"
table1::label(d$b4ca) <- "Stroke"
table1::label(d$b4da) <- "Hypertension"
table1::label(d$b4ea) <- "Peripheral_arterial"
table1::label(d$b4fa) <- "High_cholesterol"
table1::label(d$b4ga) <- "Lung"
table1::label(d$b4ha) <- "Stomach"
table1::label(d$b4ia) <- "Bowel"
table1::label(d$b4ja) <- "Diabetes"
table1::label(d$b4ka) <- "Kidney"
table1::label(d$b4la) <- "Liver"
table1::label(d$b4ma) <- "Arthritis"
table1::label(d$b4na) <- "Alzheimers"
table1::label(d$b4oa) <- "Depression"
table1::label(d$b4pa) <- "AIDS"
table1::label(d$b4qa) <- "Other_Cancers"
table1(~ b4aa+b4ba+b4ca+b4da+b4ea+b4fa+b4ga+b4ha+b4ia+b4ja+b4ka+b4la+b4ma+b4na+b4oa+b4pa+b4qa | aggressiveness_grant, extra.col=list('P-value'=pvalue),
       data=d, topclass="Rtable1-shade", overall=FALSE)

table1(~ Comorbidity_Score + Comorbidity_Any | aggressiveness_grant, extra.col=list('P-value'=pvalue),
       data=d, topclass="Rtable1-shade", overall=FALSE)

```

### By Lifestyle Factors
```{r agg_grant by lifestyle factors, results='asis'}

table1::label(d$f3) <- "Excercise_days_per_week"
table1::label(d$f4) <- "Excercise_amount"
table1::label(d$f5) <- "Drinking_per_week"
table1::label(d$f6) <- "Drinking_amount"
table1::label(d$f7) <- "Smoking"
table1::label(d$f7a) <- "Smoking_amount"
table1(~ f3+f4+f5+f6+f7+f7a | aggressiveness_grant, extra.col=list('P-value'=pvalue),
       data=d, topclass="Rtable1-shade", overall=FALSE)

```


## Aggressiveness ('Epi')
### By Cancer History
```{r agg_epi by cancers, results='asis'}
table1(~ Breast_Yes+Ovarian_Yes+Colorectal_Yes+Lung_Yes+Other_Cancer_Yes+Any_Cancer_Yes | aggressiveness_epi, extra.col=list('P-value'=pvalue), data=d, topclass="Rtable1-shade", overall=FALSE)

```

### By Comorbidities
```{r agg_Epi by comoridities, results='asis'}

table1::label(d$b4aa) <- "Heart_Attack"
table1::label(d$b4ba) <- "Heart_Failure"
table1::label(d$b4ca) <- "Stroke"
table1::label(d$b4da) <- "Hypertension"
table1::label(d$b4ea) <- "Peripheral_arterial"
table1::label(d$b4fa) <- "High_cholesterol"
table1::label(d$b4ga) <- "Lung"
table1::label(d$b4ha) <- "Stomach"
table1::label(d$b4ia) <- "Bowel"
table1::label(d$b4ja) <- "Diabetes"
table1::label(d$b4ka) <- "Kidney"
table1::label(d$b4la) <- "Liver"
table1::label(d$b4ma) <- "Arthritis"
table1::label(d$b4na) <- "Alzheimers"
table1::label(d$b4oa) <- "Depression"
table1::label(d$b4pa) <- "AIDS"
table1::label(d$b4qa) <- "Other_Cancers"
table1(~ b4aa+b4ba+b4ca+b4da+b4ea+b4fa+b4ga+b4ha+b4ia+b4ja+b4ka+b4la+b4ma+b4na+b4oa+b4pa+b4qa | aggressiveness_epi, extra.col=list('P-value'=pvalue),
       data=d, topclass="Rtable1-shade", overall=FALSE)

```

### By Lifestyle Factors
```{r agg_epi by lifestyle factors, results='asis'}

table1::label(d$f3) <- "Excercise_days_per_week"
table1::label(d$f4) <- "Excercise_amount"
table1::label(d$f5) <- "Drinking_per_week"
table1::label(d$f6) <- "Drinking_amount"
table1::label(d$f7) <- "Smoking"
table1::label(d$f7a) <- "Smoking_amount"
table1(~ f3+f4+f5+f6+f7+f7a | aggressiveness_epi, extra.col=list('P-value'=pvalue),
       data=d, topclass="Rtable1-shade", overall=FALSE)

```


## Aggressiveness ("D'Amico")
### By Cancer History
```{r agg_D_Amico by cancers, results='asis'}
table1(~ Breast_Yes+Ovarian_Yes+Colorectal_Yes+Lung_Yes+Other_Cancer_Yes+Any_Cancer_Yes | D_Amico_risk_groups, extra.col=list('P-value'=pvalue), data=d, topclass="Rtable1-shade", overall=FALSE)

```

### By Comorbidities
```{r agg_D_Amico by comoridities, results='asis'}

table1::label(d$b4aa) <- "Heart_Attack"
table1::label(d$b4ba) <- "Heart_Failure"
table1::label(d$b4ca) <- "Stroke"
table1::label(d$b4da) <- "Hypertension"
table1::label(d$b4ea) <- "Peripheral_arterial"
table1::label(d$b4fa) <- "High_cholesterol"
table1::label(d$b4ga) <- "Lung"
table1::label(d$b4ha) <- "Stomach"
table1::label(d$b4ia) <- "Bowel"
table1::label(d$b4ja) <- "Diabetes"
table1::label(d$b4ka) <- "Kidney"
table1::label(d$b4la) <- "Liver"
table1::label(d$b4ma) <- "Arthritis"
table1::label(d$b4na) <- "Alzheimers"
table1::label(d$b4oa) <- "Depression"
table1::label(d$b4pa) <- "AIDS"
table1::label(d$b4qa) <- "Other_Cancers"
table1(~ b4aa+b4ba+b4ca+b4da+b4ea+b4fa+b4ga+b4ha+b4ia+b4ja+b4ka+b4la+b4ma+b4na+b4oa+b4pa+b4qa | D_Amico_risk_groups, extra.col=list('P-value'=pvalue),
       data=d, topclass="Rtable1-shade", overall=FALSE)

```

### By Lifestyle Factors
```{r agg_D_Amico by lifestyle factors, results='asis'}

table1::label(d$f3) <- "Excercise_days_per_week"
table1::label(d$f4) <- "Excercise_amount"
table1::label(d$f5) <- "Drinking_per_week"
table1::label(d$f6) <- "Drinking_amount"
table1::label(d$f7) <- "Smoking"
table1::label(d$f7a) <- "Smoking_amount"
table1(~ f3+f4+f5+f6+f7+f7a | D_Amico_risk_groups, extra.col=list('P-value'=pvalue),
       data=d, topclass="Rtable1-shade", overall=FALSE)

```

