---
title: "RESPOND Data Investigation"
author: "David Conti and Rich Pinder"
date: "`r Sys.time()`"
output:
  html_document:
    df_print: paged
    code_folding: hide
  pdf_document: default
---

```{r setup, include=FALSE, echo=FALSE}
require("RPostgreSQL") # for PostgreSQL
library(zoo) # for date conversion
library(expss) # for labels
library(DBI) # for Database connectivity
library(summarytools) # for summarizing variables
library(tidyverse)
library(plyr)
library(knitr) # for creating tables
# set working directory
setwd("~/Google Drive File Stream/My Drive/Projects/RESPOND/CORE D/InitalDataCleaning")

```

```{r input registry data, echo=FALSE}
load("VRegAll20210116.Rda")
d <- VRegAll
#print(names(d))
```

```{r first look - registry data - 30 vars, echo=FALSE}
varName.list <- names(d)
varName.list <- c("registryid",
                  "birthplace","birthplacestate","birthplacecountry",
                  "dateofdiagnosis",
                  "primarysite", "grade",
                  "typeofreportingsource","primarypayeratdx",
                  "derivedsummarystage2018","derivedeod2018stagegroup",
                  "rxsummtreatmentstatus","rxsummsurgprimsite","rxsummradiation","rxsummchemo","rxsummhormone",
                  "vitalstatus",
                  "derivedss2000","derivedajcc7stagegrp","derivedseercmbstggrp",
                  "gleasonpatternsclinical","gleasonpatternspathological","gleasonscoreclinical","gleasonscorepathological","gleasontertiarypattern",
                  "gradeclinical","gradepathological",
                  "numberofcoresexamined","numberofcorespositive",
                  "prostatepathologicalextension",
                  "psalabvalue")
d <- d[,varName.list]
print(names(d))
print(dim(d))

new.d <- data.frame(matrix(ncol=0, nrow=nrow(d)))
new.d.n <- data.frame(matrix(ncol=0, nrow=nrow(d)))
new.d.1 <- data.frame(matrix(ncol=0, nrow=nrow(d)))

```

# REGISTRY ID	
http://datadictionary.naaccr.org/default.aspx?c=10&Version=18#40  
A unique code that represents the data transmission source. This item should be used for central registries and non-US health care providers. Refer to Registry ID table in Appendix B.

```{r registryid }

if("registryid" %in% varName.list) { 
  registryid <- as.factor(trimws(d[,"registryid"]))
  #new.d.n <- data.frame(new.d.n, registryid) # keep NAACCR coding
  
  # NEED REGISTRY NAMES!!
 
  
  #replace number with names
  
  levels(registryid)[levels(registryid)=="1501"] <- "SEER San Francisco-Oakland SMSA"
  levels(registryid)[levels(registryid)=="1527"] <- "SEER Metropolitan Atlanta"
  levels(registryid)[levels(registryid)=="1535"] <- "SEER Los Angeles"
  levels(registryid)[levels(registryid)=="1537"] <- "SEER Rural Georgia"
  levels(registryid)[levels(registryid)=="1541"] <- "SEER California except LA, SF-Oak, and San-Jose/Monterey"
  levels(registryid)[levels(registryid)=="1547"] <- "SEER Greater Georgia"
  levels(registryid)[levels(registryid)=="60"] <- "Registry7"
  levels(registryid)[levels(registryid)=="7300"] <- "Louisiana Tumor Registry"
  
  
  new.d <- data.frame(new.d, registryid)
  new.d <- apply_labels(new.d, registryid = "Registry ID")
  new.d.1 <- data.frame(new.d.1, registryid)
  
  #cro(new.d$registryid) # this is pretty but doesn't show NAs
  #summary(new.d$registryid)
  
  #Using kable function to form a nice table
  
  registryid_count<-count(new.d$registryid)
  colnames(registryid_count)<- c("Registry", "Total")
  kable(registryid_count, format = "html", align = 'c')
  }

```

# BIRTHPLACE
http://datadictionary.naaccr.org/default.aspx?c=10&Version=18#250  
Description
Code for place of birth of the patient. If a patient has multiple tumors, all records should contain the same code.  
Rationale  
Place of Birth is helpful for patient matching and can be used when reviewing race and ethnicity. In addition, adding birthplace data to race and ethnicity allows for a more specific definition of the population being reported. Careful descriptions of ancestry, birthplace, and immigration history of populations studied are needed to make the basis for classification into ethnic groups clear. Birthplace has been associated with variation in genetic, socioeconomic, cultural, and nutritional characteristics that affect patterns of disease. A better understanding of the differences within racial and ethnic categories also can help states develop effective, culturally sensitive public health prevention programs to decrease the prevalence of high-risk behaviors and increase the use of preventive services.  
Note: For cases diagnosed January 1, 2013, and later, Birthplace--State [252] and Birthplace--Country [254] replace Birthplace [250].  
Codes  
See Appendix B  for numeric and alphabetic lists of places and codes (also see Appendix B of the SEER Program Code Manual at seer.cancer.gov/tools/codingmanuals/index.html).
```{r birthplace }

if("birthplace" %in% varName.list) { 
  birthplace <- as.factor(trimws(d[,"birthplace"]))
  # recode for interpretable birthplace
  #new.d.n <- data.frame(new.d.n, birthplace) # keep NAACCR coding
  levels(birthplace)[levels(birthplace)=="999"] <- "Unkown"
  levels(birthplace)[levels(birthplace)=="97"] <- "Sonoma (Greater California)"


  new.d <- data.frame(new.d, birthplace)
  new.d <- apply_labels(new.d, birthplace = "Place of birth")
  
  cro(new.d$birthplace)
  #cro(new.d$registryid, new.d$birthplace)
  
  }

```

# BIRTHPLACE--STATE
USPS abbreviation for the state, commonwealth, U.S. possession; or CanadaPost abbreviation for the Canadian province/territory in which the patient was born. If the patient has multiple primaries, the state of birth is the same for each tumor. This data item became part of the NAACCR transmission record effective with Volume II, Version 13 in order to include country and state for each geographic item and to use interoperable codes. It supplements the item BIRTHPLACE--COUNTRY [254]. These two data items are intended to replace the item BIRTHPLACE [250].  
Rationale  
This is a modification of the current item Birthplace [250] item in order to make use of standard codes, rather than using geographic codes that are only used by cancer registries. The intention is that item 250 be converted to populate the new corresponding, more standard, data items.
Codes  
See Appendix B for numeric and alphabetic lists of places and codes (also see Appendix B of the SEER Program Code Manual at seer.cancer.gov/tools/codingmanuals/index.html).
```{r birthplace state }

if("birthplacestate" %in% varName.list) {
  birthplacestate <- as.factor(trimws(d[,"birthplacestate"]))
  # recode for interpretable birthplace state
  #new.d.n <- data.frame(new.d.n, birthplacestate) # keep NAACCR coding
  
  levels(birthplacestate)[levels(birthplacestate)=="AK"] <- "Alaska"
  levels(birthplacestate)[levels(birthplacestate)=="AL"] <- "Alabama"
  levels(birthplacestate)[levels(birthplacestate)=="AR"] <- "Arkansas"
  levels(birthplacestate)[levels(birthplacestate)=="AZ"] <- "Arizona"
  levels(birthplacestate)[levels(birthplacestate)=="CA"] <- "California"
  levels(birthplacestate)[levels(birthplacestate)=="CD"] <- "Canada"
  levels(birthplacestate)[levels(birthplacestate)=="CO"] <- "Colorado"
  levels(birthplacestate)[levels(birthplacestate)=="CT"] <- "Connecticut"
  levels(birthplacestate)[levels(birthplacestate)=="DC"] <- "District of Columbia"
  levels(birthplacestate)[levels(birthplacestate)=="DE"] <- "Delaware"
  levels(birthplacestate)[levels(birthplacestate)=="FL"] <- "Florida"
  levels(birthplacestate)[levels(birthplacestate)=="GA"] <- "Georgia"
  levels(birthplacestate)[levels(birthplacestate)=="GU"] <- "Guam"
  levels(birthplacestate)[levels(birthplacestate)=="HI"] <- "Hawaii"
  levels(birthplacestate)[levels(birthplacestate)=="IA"] <- "Iowa"
  levels(birthplacestate)[levels(birthplacestate)=="IL"] <- "Illinois"
  levels(birthplacestate)[levels(birthplacestate)=="IN"] <- "Indiana"
  levels(birthplacestate)[levels(birthplacestate)=="KS"] <- "Kansas"
  levels(birthplacestate)[levels(birthplacestate)=="KY"] <- "Kentucky"
  levels(birthplacestate)[levels(birthplacestate)=="LA"] <- "Louisiana"
  levels(birthplacestate)[levels(birthplacestate)=="MA"] <- "Massachusetts"
  levels(birthplacestate)[levels(birthplacestate)=="MD"] <- "Maryland"
  levels(birthplacestate)[levels(birthplacestate)=="ME"] <- "Maine"
  levels(birthplacestate)[levels(birthplacestate)=="MI"] <- "Michigan"
  levels(birthplacestate)[levels(birthplacestate)=="MN"] <- "Minnesota"
  levels(birthplacestate)[levels(birthplacestate)=="MO"] <- "Missouri"
  levels(birthplacestate)[levels(birthplacestate)=="MS"] <- "Mississippi"
  levels(birthplacestate)[levels(birthplacestate)=="MT"] <- "Montana"
  levels(birthplacestate)[levels(birthplacestate)=="NC"] <- "North Carolina"
  levels(birthplacestate)[levels(birthplacestate)=="NE"] <- "Nebraska"
  levels(birthplacestate)[levels(birthplacestate)=="NJ"] <- "New Jersey"
  levels(birthplacestate)[levels(birthplacestate)=="NM"] <- "New Mexico"
  levels(birthplacestate)[levels(birthplacestate)=="NY"] <- "New York"
  levels(birthplacestate)[levels(birthplacestate)=="OH"] <- "Ohio"
  levels(birthplacestate)[levels(birthplacestate)=="OK"] <- "Oklahoma"
  levels(birthplacestate)[levels(birthplacestate)=="OR"] <- "Oregon"
  levels(birthplacestate)[levels(birthplacestate)=="PA"] <- "Pennsylvania"
  levels(birthplacestate)[levels(birthplacestate)=="PR"] <- "Puerto Rico"
  levels(birthplacestate)[levels(birthplacestate)=="SC"] <- "South Carolina"
  levels(birthplacestate)[levels(birthplacestate)=="SD"] <- "South Dakota"
  levels(birthplacestate)[levels(birthplacestate)=="TN"] <- "Tennessee"
  levels(birthplacestate)[levels(birthplacestate)=="TX"] <- "Texas"
  levels(birthplacestate)[levels(birthplacestate)=="US"] <- "United States of America (the)"
  levels(birthplacestate)[levels(birthplacestate)=="UT"] <- "Utah"
  levels(birthplacestate)[levels(birthplacestate)=="VA"] <- "Virginia"
  levels(birthplacestate)[levels(birthplacestate)=="VI"] <- "Virgin Islands (U.S.)"
  levels(birthplacestate)[levels(birthplacestate)=="VT"] <- "Vermont"
  levels(birthplacestate)[levels(birthplacestate)=="WA"] <- "Washington"
  levels(birthplacestate)[levels(birthplacestate)=="WI"] <- "Wisconsin"
  levels(birthplacestate)[levels(birthplacestate)=="WV"] <- "West Virginia"
  #levels(birthplacestate)[levels(birthplacestate)=="XX"] <- ""
  #levels(birthplacestate)[levels(birthplacestate)=="YY"] <- ""
  levels(birthplacestate)[levels(birthplacestate)=="ZZ"] <- "Unknown"

  new.d <- data.frame(new.d, birthplacestate)
  new.d <- apply_labels(new.d, birthplacestate = "State of birth")
  
  #summarytools::view(dfSummary(temp.d, style = 'grid', max.distinct.values = 100), method = 'render', report.title = 'All Data')
  #lapply(unique(temp.d$registryid), FUN = function(loc){
   # summarytools::view(dfSummary(temp.d[new.d$registryid == loc, ], style = 'grid', max.distinct.values = 100),
                       #method = 'render', report.title = as.character(loc))
  #})
  
  
  
  cro(new.d$birthplacestate)
  #cro(new.d$registryid, new.d$birthplacestate)
  
  }

```

```{r birthplacestate smry}

#Works well in RStudio, but not in HTML file
temp.d <- data.frame (new.d.1, birthplacestate)
summarytools::view(dfSummary(temp.d$birthplacestate, style = 'grid', max.distinct.values = 100, tmp.img.dir = "/tmp", report.title = 'All Data'))
lapply(unique(new.d$registryid), FUN = function(loc){
   summarytools::view(dfSummary(temp.d[new.d$registryid == loc, ], style = 'grid', max.distinct.values = 100, tmp.img.dir = "/tmp"),
                       method = 'render', report.title = as.character(loc))
})
rm(temp.d)
```




# BIRTHPLACE--COUNTRY
Code for the country in which the patient was born. If the patient has multiple tumors, all records should contain the same code. This data item became part of the NAACCR transmission record effective with Volume II, Version 13 in order to include country and state for each geographic item and to use interoperable codes. It supplements the item BIRTHPLACE--STATE [252]. These two data items are intended to replace the use of BIRTHPLACE [250].  
Rationale  
Place of Birth is helpful for patient matching and can be used when reviewing race and ethnicity. It is an important item in algorithms for imputing race and ethnicity. In addition, adding birthplace data to race and ethnicity allows for a more specific definition of the population being reported. Careful descriptions of ancestry, birthplace, and immigration history of populations studied are needed to make the basis for classification into ethnic groups clear. Birthplace has been associated with variation in genetic, socioeconomic, cultural, and nutritional characteristics that affect patterns of disease. A better understanding of the differences within racial and ethnic categories also can help states develop effective, culturally-sensitive public health prevention programs to decrease the prevalence of high-risk behaviors and increase the use of preventive services.  
Codes  
Custom codes for historic use only  
ZZN	North America NOS
ZZC	Central American NOS
ZZS	South America NOS
ZZP	Pacific NOS
ZZE	Europe NOS
ZZF	Africa NOS
ZZA	Asia NOS
ZZX	Non-US NOS
ZZU	Unknown
Custom codes for historic use only
XNI	North American Islands
XCB	Other Caribbean Islands
XEN	England, Channel Islands, Isle of Man
XSC	Scandinavia
XGR	Germanic Countries
XSL	Slavic Countries
CSK	Czechoslovakia (former)
YUG	Yugoslavia (former)
XUM	Ukraine and Moldova
XNF	North Africa
XSD	Sudanese Countries
XWF	West Africa
XSF	South Africa
XEF	East Africa
XIF	African Islands
XET	Ethiopia and Eritrea
XAP	Arabian Peninsula
XIS	Israel and Palestine
XCR	Caucasian Republics of former USSR
XOR	Other Asian Republics of former USSR
XSE	Southeast Asia
XMS	Malaysia, Singapore, Brunei
XCH	China, NOS
XML	Melanesian Islands
XMC	Micronesian Islands
XPL	Polynesian Islands  
See Appendix B for numeric and alphabetic lists of places and codes (also see Appendix B of the SEER Program Code Manual at seer.cancer.gov/tools/codingmanuals/index.html).
```{r birthplace country }

if("birthplacecountry" %in% varName.list) {
  birthplacecountry <- as.factor(trimws(d[,"birthplacecountry"]))
  #new.d.n <- data.frame(new.d.n, birthplacecountry) # keep NAACCR coding
  # recode for interpretable birthplace country
  levels(birthplacecountry)[levels(birthplacecountry)=="ZZU"] <- "Unkown"
  levels(birthplacecountry)[levels(birthplacecountry)=="ZZF"] <- "Africa"
  levels(birthplacecountry)[levels(birthplacecountry)=="ZZX"] <- "Non_US"
  levels(birthplacecountry)[levels(birthplacecountry)=="ZZE"] <- "Europe NOS"
  levels(birthplacecountry)[levels(birthplacecountry)=="ZZC"] <- "Central American NOS"
  levels(birthplacecountry)[levels(birthplacecountry)=="ZWE"] <- "Zimbabwe"
  levels(birthplacecountry)[levels(birthplacecountry)=="XWF"] <- "West Africa, NOS (French Africa, NOS)"
  levels(birthplacecountry)[levels(birthplacecountry)=="WSM"] <- "Samoa"
  levels(birthplacecountry)[levels(birthplacecountry)=="VIR"] <- "Virgin Islands (U.S.)"
  levels(birthplacecountry)[levels(birthplacecountry)=="USA"] <- "United States of America (the)"
  levels(birthplacecountry)[levels(birthplacecountry)=="UGA"] <- "Uganda"
  levels(birthplacecountry)[levels(birthplacecountry)=="TTO"] <- "Trinidad and Tobago"
  levels(birthplacecountry)[levels(birthplacecountry)=="SOM"] <- "Somalia"
  levels(birthplacecountry)[levels(birthplacecountry)=="SLE"] <- "Sierra Leone"
  levels(birthplacecountry)[levels(birthplacecountry)=="SEN"] <- "Senegal"
  levels(birthplacecountry)[levels(birthplacecountry)=="RWA"] <- "Rwanda"
  levels(birthplacecountry)[levels(birthplacecountry)=="PRT"] <- "Portugal"
  levels(birthplacecountry)[levels(birthplacecountry)=="PRI"] <- "Puerto Rico"
  levels(birthplacecountry)[levels(birthplacecountry)=="PAN"] <- "Panama"
  levels(birthplacecountry)[levels(birthplacecountry)=="NIC"] <- "Nicaragua"
  levels(birthplacecountry)[levels(birthplacecountry)=="NGA"] <- "Nigeria"
  levels(birthplacecountry)[levels(birthplacecountry)=="NER"] <- "Niger"
  levels(birthplacecountry)[levels(birthplacecountry)=="MEX"] <- "Mexico"
  levels(birthplacecountry)[levels(birthplacecountry)=="LCA"] <- "Saint Lucia"
  levels(birthplacecountry)[levels(birthplacecountry)=="LBR"] <- "Liberia"
  levels(birthplacecountry)[levels(birthplacecountry)=="JPN"] <- "Japan"
  levels(birthplacecountry)[levels(birthplacecountry)=="JAM"] <- "Jamaica"
  levels(birthplacecountry)[levels(birthplacecountry)=="HUN"] <- "Hungary"
  levels(birthplacecountry)[levels(birthplacecountry)=="HTI"] <- "Haiti"
  levels(birthplacecountry)[levels(birthplacecountry)=="GUY"] <- "Guyana"
  levels(birthplacecountry)[levels(birthplacecountry)=="GUM"] <- "Guam"
  levels(birthplacecountry)[levels(birthplacecountry)=="GRD"] <- "Grenada"
  levels(birthplacecountry)[levels(birthplacecountry)=="GMB"] <- "Gambia (the)"
  levels(birthplacecountry)[levels(birthplacecountry)=="GHA"] <- "Ghana"
  levels(birthplacecountry)[levels(birthplacecountry)=="GEO"] <- "Georgia"
  levels(birthplacecountry)[levels(birthplacecountry)=="GBR"] <- "United Kingdom of Great Britain and Northern Ireland (the)"
  levels(birthplacecountry)[levels(birthplacecountry)=="FRA"] <- "France"
  levels(birthplacecountry)[levels(birthplacecountry)=="ETH"] <- "Ethiopia"
  levels(birthplacecountry)[levels(birthplacecountry)=="ERI"] <- "Eritrea"
  levels(birthplacecountry)[levels(birthplacecountry)=="ENG"] <- "England"
  levels(birthplacecountry)[levels(birthplacecountry)=="DOM"] <- "Dominican Republic (the)"
  levels(birthplacecountry)[levels(birthplacecountry)=="DEU"] <- "Germany"
  levels(birthplacecountry)[levels(birthplacecountry)=="CUB"] <- "Cuba"
  levels(birthplacecountry)[levels(birthplacecountry)=="CRI"] <- "Costa Rica"
  levels(birthplacecountry)[levels(birthplacecountry)=="COG"] <- "Congo (the)"
  levels(birthplacecountry)[levels(birthplacecountry)=="CMR"] <- "Cameroon"
  levels(birthplacecountry)[levels(birthplacecountry)=="CIV"] <- "Cote d'Ivoire"
  levels(birthplacecountry)[levels(birthplacecountry)=="CAN"] <- "Canada"
  levels(birthplacecountry)[levels(birthplacecountry)=="BRB"] <- "Barbados"
  levels(birthplacecountry)[levels(birthplacecountry)=="BLZ"] <- "Belize"
  levels(birthplacecountry)[levels(birthplacecountry)=="BHS"] <- "Bahamas (the)"
  levels(birthplacecountry)[levels(birthplacecountry)=="ARE"] <- "United Arab Emirates (the)"

  
  new.d <- data.frame(new.d, birthplacecountry)
  new.d <- apply_labels(new.d, birthplacecountry = "Country of birth")
  
  cro(new.d$birthplacecountry)
  #cro(new.d$registryid, new.d$birthplacecountry)
  
  }

```

```{r birthplacecountry smry}
temp.d <- data.frame (new.d.1, birthplacecountry)
summarytools::view(dfSummary(temp.d$birthplacecountry, style = 'grid', max.distinct.values = 100, report.title = 'All Data'))
lapply(unique(new.d$registryid), FUN = function(loc){
   summarytools::view(dfSummary(temp.d[new.d$registryid == loc, ], style = 'grid', max.distinct.values = 100),
                       method = 'render', report.title = as.character(loc))
})
rm(temp.d)
```

# DATE OF DIAGNOSIS
Date of initial diagnosis by a recognized medical practitioner for the tumor being reported whether clinically or microscopically confirmed. See Chapter X for date format.
```{r data of diagnosis }
if("dateofdiagnosis" %in% varName.list) {
  dateofdiagnosis <- trimws(d[,"dateofdiagnosis"])
  #new.d.n <- data.frame(new.d.n, dateofdiagnosis) # keep NAACCR coding
  
  select99 <- substr(dateofdiagnosis, start=7, stop=8)=="99"
  dateofdiagnosis[select99] <- substr(dateofdiagnosis[select99], start=1, stop=6)
  select6 <- nchar(trimws(dateofdiagnosis))==6
  dateofdiagnosis[select6] <- as.Date(as.yearmon(dateofdiagnosis[select6], c("%Y%m")))
  select8 <- nchar(trimws(dateofdiagnosis))==8
  dateofdiagnosis[select8] <- as.Date(dateofdiagnosis[select8], c("%Y%m%d"))
  
  dateofdiagnosis <- as.Date(as.numeric(dateofdiagnosis), origin = "1970-01-01")
  new.d <- data.frame(new.d, dateofdiagnosis)
  new.d <- apply_labels(new.d, dateofdiagnosis = "Date of Diagnosis")
  summary(new.d$dateofdiagnosis)
  
  
  #by(new.d$dateofdiagnosis, new.d$registryid, summary)
}
temp.d <- data.frame (new.d.1, dateofdiagnosis)

lapply(unique(new.d$registryid), FUN = function(loc){
   summary(temp.d[new.d$registryid == loc, ])
})
rm(temp.d)

```

# PRIMARY SITE
Code for the primary site of the tumor being reported using either ICD-O-2 or ICD-O-3. NAACCR adopted ICD-O-2 as the standard coding system for tumors diagnosed beginning January 1, 1992. In addition, NAACCR recommended that tumors diagnosed prior to 1992 be converted to ICD-O-2. The topography (primary site) codes did not change between ICD-O-2 and ICD-O-3.
```{r primary site of tumor }
if("primarysite" %in% varName.list) {
  primarysite <- as.factor(d[,"primarysite"])
  levels(primarysite) <- list(Prostate="C619") # other codings become NA
  new.d <- data.frame(new.d, primarysite)
  new.d <- apply_labels(new.d, primarysite = "Primary Tumor Site")
  
  cro(new.d$primarysite)# this is pretty but doesn't show NAs
  summary(new.d$primarysite)
}

```

# GRADE
Code for the grade or degree of differentiation of the reportable tumor. For lymphomas and leukemias, field also is used to indicate T-, B-, Null-, or NK-cell origin.  
See the grade tables on page 67 of ICD-O-3.16 See also the most recent CoC STORE manual and SEER Program Code Manual, for site specific coding rules and conversions.

1	Grade I  
2	Grade II  
3	Grade III  
4	Grade IV  
5	T-cell  
6	B-cell  
7	Null cell  
8	NK (natural killer) cell  
9	Grade/differentiation unknown, not stated, or not applicable  
Comment: Use the most recent Hematopoietic and Lymphoid rules for assigning grades 5-8.  
```{r grade }
if("grade" %in% varName.list) {
  grade <- as.factor(d[,"grade"])
  levels(grade) <- list(Grade_I="1",
                        Grade_II="2",
                        Grade_III="3",
                        Grade_IV="4",
                        T_cell="5",
                        B_cell="6",
                        Null_cell="7",
                        NK_cell="8",
                        Unknown="9")
  new.d <- data.frame(new.d, grade)
  new.d <- apply_labels(new.d, grade = "Tumor Grade")
  
  cro(new.d$grade)# this is pretty but doesn't show NAs
  #summary(new.d$grade)
  summarytools::freq(new.d$grade, style = "rmarkdown")


}

```

# TYPE OF REPORTING SOURCE
This variable codes the source documents used to abstract the majority of information on the tumor being reported. This may not be the source of original case finding (for example, if a case is identified through a pathology laboratory report review and all source documents used to abstract the case are from the physician’s office, code this item 4).  

Rationale
The code in this field can be used to explain why information may be incomplete on a tumor. For example, death certificate only cases have unknown values for many data items, so one may want to exclude them from some analyses. The field also is used to monitor the success of non-hospital case reporting and follow-back mechanisms. All population-based registries should have some death certificate-only cases where no hospital admission was involved, but too high a percentage can imply both shortcomings in case-finding and that follow-back to uncover missed hospital reports was not complete.

Coding Instructions
Code in the following priority order: 1, 2, 8, 4, 3, 5, 6, 7. This is a change to reflect the addition of codes 2 and 8 and to prioritize laboratory reports over nursing home reports. The source facilities included in the previous code 1 (hospital inpatient and outpatient) are split between codes 1, 2, and 8.

This data item is intended to indicate the completeness of information available to the abstractor. Reports from health plans (e.g., Kaiser, Veterans Administration, military facilities) in which all diagnostic and treatment information is maintained centrally and is available to the abstractor are expected to be at least as complete as reports for hospital inpatients, which is why these sources are grouped with inpatients and given the code with the highest priority.

Sources coded with '2' usually have complete information on the cancer diagnosis, staging, and treatment.

Sources coded with '8' would include, but would not be limited to, outpatient surgery and nuclear medicine services. A physician's office that calls itself a surgery center should be coded as a physician's office. Surgery centers are equipped and staffed to perform surgical procedures under general anesthesia. If a physician's office calls itself a surgery center, but cannot perform surgical procedures under general anesthesia, code as a physician office.

Codes
1	Hospital inpatient; Managed health plans with comprehensive, unified medical records
2	Radiation Treatment Centers or Medical Oncology Centers (hospital-affiliated or independent)
3	Laboratory only (hospital-affiliated or independent)
4	Physician's office/private medical practitioner (LMD)
5	Nursing/convalescent home/hospice
6	Autopsy only
7	Death certificate only
8	Other hospital outpatient units/surgery centers
```{r type of reporting source}
if("typeofreportingsource" %in% varName.list) {
  typeofreportingsource <- as.factor(d[,"typeofreportingsource"])
  levels(typeofreportingsource) <- list(Hospital="1",
                                 Radiation_Tx="2",
                                 Laboratory_Only="3",
                                 Physician="4",
                                 Nursing="5",
                                 Autopsy="6",
                                 Death_Certificate="7",
                                 Other_Hospital_Unit="8")
  new.d <- data.frame(new.d, typeofreportingsource)
  new.d <- apply_labels(new.d, typeofreportingsource = "Source of Tumor Information")
  
  #summary(new.d$typeofreportingsource)
    summarytools::freq(new.d$typeofreportingsource, style = "rmarkdown")

  
}

```

                  
# PRIMARY PAYER AT DX
Description  
Primary payer/insurance carrier at the time of initial diagnosis and/or treatment at the reporting facility.

Rationale  
This item is used in financial analysis and as an indicator for quality and outcome analyses.

Codes  
01	Not insured  
02	Not insured, self-pay  
10	Insurance, NOS  
20	Private Insurance: Managed care, HMO, or PPO  
21	Private Insurance: Fee-for-Service  
31	Medicaid  
35	Medicaid - Administered through a Managed Care plan  
60	Medicare/Medicare, NOS  
61	Medicare with supplement, NOS  
62	Medicare - Administered through a Managed Care plan  
63	Medicare with private supplement  
64	Medicare with Medicaid eligibility  
65	TRICARE  
66	Military  
67	Veterans Affairs  
68	Indian/Public Health Service  
99	Insurance status unknown
```{r primary payer at dx }
if("primarypayeratdx" %in% varName.list) {
  primarypayeratdx <- as.factor(d[,"primarypayeratdx"])
  levels(primarypayeratdx) <- list(Not_insured="1",
                               Not_insured_self_pay="2",
                               Insurance="10",
                               Private_managed="20",
                               Private_FFS="21", # fee-for-service
                               Medicaid="31",
                               Medicaid_managed_care="35",
                               Medicare_medicare="60",
                               Medicare_suppl="61",
                               Medicare_managed_care="62",
                               Medicare_private_suppl="63",
                               Medicare_medicaid="64",
                               TRICARE="65",
                               Military="66",
                               Veterans_Affairs="67",
                               Indian_PHS="68",
                               Unknown="99")
    primarypayeratdx <- relevel(primarypayeratdx, ref="Private_managed")
    new.d <- data.frame(new.d, primarypayeratdx)
    new.d <- apply_labels(new.d, primarypayeratdx = "Primary payer/insurance at the time of diagnosis")
    #summary(new.d$primarypayeratdx)
    summarytools::freq(new.d$primarypayeratdx, style = "rmarkdown")

}

```

# DERIVED SUMMARY STAGE 2018
Description  
Derived Summary Stage 2018 is derived using the EOD data collection system (EOD Primary Tumor [772], EOD Regional Nodes [774] and EOD Mets [776]) algorithm. Other data items may be included in the derivation process. Effective for cases diagnosed 1/1/2018+.

Rationale  
The SEER program has collected staging information on cases since its inception in 1973. Summary Stage groups cases into broad categories of in situ, local, regional, and distant. Summary Stage can be used to evaluate disease spread at diagnosis, treatment patterns and outcomes over time.
 
Derived Summary Stage 2018 [762] is only available at the central registry level.
Note: This data item was included in Standards Volume II, Version 16; however, it was not implemented until 2018.

Codes  
0	In situ  
1	Localized  
2	Regional, direct extension only  
3	Regional, regional lymph nodes only  
4	Regional, direct extension and regional lymph nodes  
7	Distant  
8	Benign, borderline  
9	Unknown if extension or metastasis (unstaged, unknown, or unspecified)  
Death certificate only case  
```{r derived summary stage 2018 }
if("derivedsummarystage2018" %in% varName.list) {
  derivedsummarystage2018 <- as.factor(d[,"derivedsummarystage2018"])
  levels(derivedsummarystage2018) <- list(In_situ="0",
                                          Localized="1",
                                          Regional_direct="2",
                                          Regional_regional="3",
                                          Regional_direct_regional="4",
                                          Distant="7",
                                          Benign_borderline="8",
                                          Unknown="9")
    derivedsummarystage2018 <- relevel(derivedsummarystage2018, ref="Localized")
    new.d <- data.frame(new.d, derivedsummarystage2018)
    new.d <- apply_labels(new.d, derivedsummarystage2018 = "Tumor Staging")
    #summary(new.d$derivedsummarystage2018)
    summarytools::freq(new.d$primarypayeratdx, style = "rmarkdown")

}

```

# DERIVED EOD 2018 STAGE GROUP
Description  
Derived EOD 2018 Stage Group is derived using the EOD data collection system (EOD Primary Tumor [772], EOD Regional Nodes [774] and EOD Mets [776]) algorithm. Other data items may be included in the derivation process. Effective for cases diagnosed 1/1/2018+.

Rationale  
Derived EOD 2018 Stage Group can be used to evaluate disease spread at diagnosis, treatment patterns and outcomes over time.
 
Derived EOD 2018 Stage group is only available at the central registry level.

Codes: See the most current version of EOD (https://staging.seer.cancer.gov/) for rules and site-specific codes and coding structures.
```{r derived EOD stage group 2018 }
if("derivedeod2018stagegroup" %in% varName.list) {
  derivedeod2018stagegroup <- as.factor(trimws(d[,"derivedeod2018stagegroup"]))
  # THIS CODING NEEDS TO BE CONFIRMED
  levels(derivedeod2018stagegroup) <- list(T1="1",
                                          T1B="1B",
                                          T2A="2A",
                                          T2B="2B",
                                          T2C="2C",
                                          T3="3",
                                          T3A="3A",
                                          T3B="3B",
                                          T3C="3C",
                                          T4="4",
                                          T4A="4A",
                                          T4B="4B",
                                          Do_Not_Know="88",
                                          Unknown="99")
    derivedeod2018stagegroup <- relevel(derivedeod2018stagegroup, ref="T1")
    new.d <- data.frame(new.d, derivedeod2018stagegroup)
    new.d <- apply_labels(new.d, derivedeod2018stagegroup = "Tumor Stage Group")
    #summary(new.d$derivedeod2018stagegroup)
    summarytools::freq(new.d$primarypayeratdx, style = "rmarkdown")

}

```

                  
# Final Summary
```{r final summary}
summarytools::view(dfSummary(new.d, style = 'grid', max.distinct.values = 100), method="browser", report.title="All Data")
lapply(unique(new.d$registryid), FUN=function(loc) { summarytools::view(dfSummary(new.d[new.d$registryid==loc,], style = 'grid', max.distinct.values = 100), method="browser", report.title = as.character(loc))})
```

