---
title: "RESPOND Data Investigation"
author: "David Conti and Rich Pinder"
date: "`r Sys.time()`"
output:
  html_document:
    df_print: paged
    code_folding: hide
  pdf_document: default
---

```{r setup, include=FALSE}
require("RPostgreSQL") # for PostgreSQL
library(zoo) # for date conversion
library(expss) # for labels
library(DBI) # for Database connectivity
library(summarytools) # for summarizing variables
library(tidyverse)
library(plyr)
# set working directory
setwd("~/Google Drive File Stream/My Drive/Projects/RESPOND/CORE D/InitalDataCleaning")

```

```{r input survey data}
load("VSurvAll20210116.Rda")
d <- VSurvAll
#print(names(d))
```


```{r first look - survey data - 108 vars, 29 questions}
varName.list <- names(d)
varName.list <- c("surveyid","locationname","respondid","methodology",
                  "a1month","a1year","a1not",
                  "a2",
                  "a3_1","a3_2","a3_3","a3_4","a3_5","a3_6","a3_7",
                  "a3_8","a3_9","a3_10","a3_11","a3_12","a3_13","a3_14","a3_15","a3_16",
                  "a3_17","a3_18","a3_19","a3_20","a3_21","a3_22","a3_23","a3_24","a3other",
                  "a4month","a4year",
                  "a8",
                  "b3",
                  "c2a1","c2a2","c2a3",
                  "c4a1","c4a2","c4a3",
                  "d1aa","d1ab","d1ba","d1bb","d1ca","d1cb","d1da","d1db","d1ea","d1eb","d1fa","d1fb","d1ga","d1gb",
                  "d3b1","d3b2","d3b3",
                  "d4a","d4b","d4c","d4d","d4e","d4f","d4g","d4h","d4i","d4j","d4k","d4l",
                  "d5a","d5b","d5c","d5d","d5e","d5f","d5g","d5h","d5i","d5j","d5k",
                  "e11a","e11b","e11c","e11d","e11e","e11f",
                  "f2lbs","f2kgs",
                  "f7","f7age","f7a","f7b","f7bage",
                  "g1","g3","g4a","g5","g7","g8",
                  "g9a","g9b","g9c",
                  "g10","g11","g12")
d <- d[,varName.list]
#print(names(d))
new.d <- data.frame(matrix(ncol=0, nrow=nrow(d)))
new.d.n <- data.frame(matrix(ncol=0, nrow=nrow(d)))

```

# SURVEY ID
Scantron assigned SurveyID
```{r survey ID }
if("surveyid" %in% varName.list) { 
  surveyid <- as.factor(d[,"surveyid"])
  isDup <- duplicated(surveyid)
  numDups <- sum(isDup)
  dups <- surveyid[isDup]
  
  new.d <- data.frame(new.d, surveyid)
  new.d <- apply_labels(new.d, surveyid = "Survey ID")
  
  print(paste("Number of duplicates:", numDups))
  print("The following are duplicated IDs:")
  print(dups)
  print("Number of NAs:")
  print(sum(is.na(new.d$surveyid)))

}

```

# LOCATION NAME
Name of Registry delivery location
```{r location name }
if("locationname" %in% varName.list) { 
  locationname <- as.factor(d[,"locationname"])
  
  tmp.d <- data.frame(locationname)
  tmp.d <- apply_labels(tmp.d, locationname = "Recruitment Location")
  #new.d <- data.frame(new.d, locationname)
  #new.d <- apply_labels(new.d, locationname = "Recruitment Location")
  
  summarytools::view(dfSummary(tmp.d, style = 'grid', max.distinct.values = 100), method="render", report.title="All Data")
  lapply(unique(tmp.d$locationname), FUN=function(loc) { summarytools::view(dfSummary(tmp.d[tmp.d$locationname==loc,], style = 'grid', max.distinct.values = 100), method="render", report.title = as.character(loc))})
  #summary(new.d$locationname)
  new.d <- data.frame(new.d, tmp.d)
  rm(tmp.d)
}

```

# RESPOND ID
From Barcode label put on last page of survey by registries, identifies participant. ResponseID is assigned by the registries.
```{r respond id }
if("respondid" %in% varName.list) { 
  respondid <- as.factor(d[,"respondid"])
  isDup <- duplicated(respondid, na.rm=T)
  numDups <- sum(isDup)
  dups <- respondid[isDup]
  
  new.d <- data.frame(new.d, respondid)
  new.d <- apply_labels(new.d, respondid = "RESPOND ID")
  
  print(paste("Number of duplicates:", numDups))
  print("The following are duplicated IDs:")
  print(dups)
  print("Number of NAs:")
  print(sum(is.na(new.d$respondid)))

}
```

# METHODOLOGY
How survey was completed  
P=Paper
O=Online complete
S=Online, started but not complete
```{r methodology }
if("methodology" %in% varName.list) { 
  methodology <- as.factor(d[,"methodology"])
  levels(methodology) <- list(Paper="P",
                              Online="O",
                              Online_not_complete="S")
  new.d <- data.frame(new.d, methodology)
  new.d <- apply_labels(new.d, methodology = "Methodology for Survey Completion")
  
  summary(new.d$methodology)
}

```

# A1
A1. In what month and year were you first diagnosed with prostate cancer?
```{r A1:month diagnosed}
if("a1month" %in% varName.list) { 
  a1month <- as.factor(d[,"a1month"])
  
  new.d <- data.frame(new.d, a1month)
  new.d <- apply_labels(new.d, a1month = "Month Diagnosed")
  
  print("a1month")
  summary(new.d$a1month)
}

if("a1year" %in% varName.list) { 
  a1year <- d[,"a1year"]
  a1year[a1year=="15"] <- "2015"  # change "15" to "2015"
  a1year <- as.Date(a1year, c("%Y"))
  
  new.d <- data.frame(new.d, a1year)
  new.d <- apply_labels(new.d, a1year = "Year Diagnosed")
  
  print("a1year")
  summary(new.d$a1year)
}

# 1=I have NEVER had prostate cancer
# 2=I HAVE or HAVE HAD prostate cancer
# (paper survey only had a bubble for “never had” so value set to 2 if bubble not marked)"
if("a1not" %in% varName.list) { 
  a1not <- as.factor(d[,"a1not"])
  levels(a1not) <- list(NEVER_had_ProstateCancer="1",
                         HAVE_had_ProstateCancer="2")
  new.d <- data.frame(new.d, a1not)
  new.d <- apply_labels(new.d, a1not = "Not Diagnosed")
  
  print("a1not")
  summary(new.d$a1not)
}
```

# A2
A2. Do you identify as Black or African American?
```{r A2:Indentify as Black or African American }
if("a2" %in% varName.list) { 
  a2 <- as.factor(d[,"a2"])
  levels(a2) <- list(Yes="2",
                     No="1")
  
  new.d <- data.frame(new.d, a2)
  new.d <- apply_labels(new.d, a2 = "Indentify as Black or African American?")
  
  summary(new.d$a2)
}
```

#A3
"If Yes:
A3. Which Black or African American group(s) and other races/ethnicities do you identify with? Mark all that apply."
```{r A3: Black or African American Groups }
if("a3_1" %in% varName.list) { a3_1 <- factor(d[,"a3_1"], levels=c(1), labels=c("Black/African American")) }
if("a3_2" %in% varName.list) { a3_2 <- factor(d[,"a3_2"], levels=c(1), labels=c("Nigerian")) }
if("a3_3" %in% varName.list) { a3_3 <- factor(d[,"a3_3"], levels=c(1), labels=c("Jamaican")) }
if("a3_4" %in% varName.list) { a3_4 <- factor(d[,"a3_4"], levels=c(1), labels=c("Ethiopian")) }
if("a3_5" %in% varName.list) { a3_5 <- factor(d[,"a3_5"], levels=c(1), labels=c("Haitian")) }
if("a3_6" %in% varName.list) { a3_6 <- factor(d[,"a3_6"], levels=c(1), labels=c("Somali")) }
if("a3_7" %in% varName.list) { a3_7 <- factor(d[,"a3_7"], levels=c(1), labels=c("Guyanese")) }
if("a3_8" %in% varName.list) { a3_8 <- factor(d[,"a3_8"], levels=c(1), labels=c("Creole")) }
if("a3_9" %in% varName.list) { a3_9 <- factor(d[,"a3_9"], levels=c(1), labels=c("West Indian")) }
if("a3_10" %in% varName.list) { a3_10 <- factor(d[,"a3_10"], levels=c(1), labels=c("Caribbean")) }
if("a3_11" %in% varName.list) { a3_11 <- factor(d[,"a3_11"], levels=c(1), labels=c("White")) }
if("a3_12" %in% varName.list) { a3_12 <- factor(d[,"a3_12"], levels=c(1), labels=c("Asian/Asian American")) }
if("a3_13" %in% varName.list) { a3_13 <- factor(d[,"a3_13"], levels=c(1), labels=c("Native American or American Indian or Alaskan Native")) }
if("a3_14" %in% varName.list) { a3_14 <- factor(d[,"a3_14"], levels=c(1), labels=c("Middle Eastern or North African")) }
if("a3_15" %in% varName.list) { a3_15 <- factor(d[,"a3_15"], levels=c(1), labels=c("Native Hawaiian or Pacific Islander")) }
if("a3_16" %in% varName.list) { a3_16 <- factor(d[,"a3_16"], levels=c(1), labels=c("Hispanic")) }
if("a3_17" %in% varName.list) { a3_17 <- factor(d[,"a3_17"], levels=c(1), labels=c("Latino")) }
if("a3_18" %in% varName.list) { a3_18 <- factor(d[,"a3_18"], levels=c(1), labels=c("Spanish")) }
if("a3_19" %in% varName.list) { a3_19 <- factor(d[,"a3_19"], levels=c(1), labels=c("Mexican/Mexican American")) }
if("a3_20" %in% varName.list) { a3_20 <- factor(d[,"a3_20"], levels=c(1), labels=c("Salvadoran")) }
if("a3_21" %in% varName.list) { a3_21 <- factor(d[,"a3_21"], levels=c(1), labels=c("Puerto Rican")) }
if("a3_22" %in% varName.list) { a3_22 <- factor(d[,"a3_22"], levels=c(1), labels=c("Dominican")) }
if("a3_23" %in% varName.list) { a3_23 <- factor(d[,"a3_23"], levels=c(1), labels=c("Columbian")) }
if("a3_24" %in% varName.list) { a3_24 <- factor(d[,"a3_24"], levels=c(1), labels=c("Other")) }
if("a3other" %in% varName.list) { 
  a3other <- d[,"a3other"]
  a3other <- as.factor(ifelse(a3other=="NA", NA, a3other))
}

new.d <- data.frame(new.d, a3_1,a3_2,a3_3,a3_4,a3_5,a3_6,a3_7,
                  a3_8,a3_9,a3_10,a3_11,a3_12,a3_13,a3_14,a3_15,a3_16,
                  a3_17,a3_18,a3_19,a3_20,a3_21,a3_22,a3_23,a3_24,a3other)   

```

# A4
A4. What is your month and year of birth?
```{r A4: Date of Birth }
if("a4month" %in% varName.list) { 
  a4month <- as.factor(d[,"a4month"])
  
  new.d <- data.frame(new.d, a4month)
  new.d <- apply_labels(new.d, a4month = "Month Birth")
  
  print("a4month")
  summary(new.d$a4month)
}

if("a4year" %in% varName.list) { 
  a4year <- d[,"a4year"]
  summary(as.factor(a4year))
  a4year <- as.Date(a4year, c("%Y"))
  
  new.d <- data.frame(new.d, a4year)
  new.d <- apply_labels(new.d, a4year = "Year Birth")
  
  print("a4year")
  summary(new.d$a4year)
}


```

# A8
A8. How many years have you lived in the United States?
1=15 years or less  
2=16-25 years  
3=My whole life or more than 25 years
```{r A8: Years in US }
if("a8" %in% varName.list) { 
  a8 <- as.factor(d[,"a8"])
  levels(a8) <- list(lt15="1",
                     bt_16_25="2",
                     gt25_life="3")
  new.d <- data.frame(new.d, a8)
  new.d <- apply_labels(new.d, a8 = "Years lived in US")
  
  summary(new.d$a8)
}
```

# B3
B3. In general, how would you rate your current health?  
1=Excellent  
2=Very Good  
3=Good  
4=Fair  
5=Poor
```{r B3: current health }
if("b3" %in% varName.list) { 
  b3 <- as.factor(d[,"b3"])
  levels(b3) <- list(Excellent="1",
                     Very_Good="2",
                     Good="3",
                     Fair="4",
                     Poor="5")
  b3 <- ordered(b3, c("Poor", "Fair", "Good", "Very_Good","Excellent"))
  
  new.d <- data.frame(new.d, b3)
  new.d <- apply_labels(new.d, b3 = "Current Health")
  
  summary(new.d$b3)
}
```

# C2
C2. Please mark answers for each of these statements.	
a. On average, I felt/feel safe walking in my neighborhood day or night.	
1=Strongly Agree  
2=Agree  
3=Neutral (neither agree nor disagree)  
4=Disagree  
5=Strongly Disagree
```{r C2: safe in neighborhood }

print("Safe in neighborhood")
if("c2a1" %in% varName.list) { 
  c2a1 <- as.factor(d[,"c2a1"])  # * gets treated as NA by not including it in levels
  levels(c2a1) <- list(Strongly_Agree="1",
                     Agree="2",
                     Neutral="3",
                     Disagree="4",
                     Strongly_Disagree="5")
  c2a1 <- ordered(c2a1, c("Strongly_Agree", "Agree", "Neutral", "Disagree","Strongly_Disagree"))
  
  new.d <- data.frame(new.d, c2a1)
  new.d <- apply_labels(new.d, c2a1 = "Safe in Neighborhood: Current")
  
  print("Current")
  summary(new.d$c2a1)
}

if("c2a2" %in% varName.list) { 
  c2a2 <- as.factor(d[,"c2a2"])  # * gets treated as NA by not including it in levels
  levels(c2a2) <- list(Strongly_Agree="1",
                     Agree="2",
                     Neutral="3",
                     Disagree="4",
                     Strongly_Disagree="5")
  c2a2 <- ordered(c2a2, c("Strongly_Agree", "Agree", "Neutral", "Disagree","Strongly_Disagree"))
  
  new.d <- data.frame(new.d, c2a2)
  new.d <- apply_labels(new.d, c2a2 = "Safe in Neighborhood: Age 31 up to just before diagnosis")
  
  print("Age 31 up to just before diagnosis")
  summary(new.d$c2a2)
}

if("c2a3" %in% varName.list) { 
  c2a3 <- as.factor(d[,"c2a3"])  # * gets treated as NA by not including it in levels
  levels(c2a3) <- list(Strongly_Agree="1",
                     Agree="2",
                     Neutral="3",
                     Disagree="4",
                     Strongly_Disagree="5")
  c2a3 <- ordered(c2a3, c("Strongly_Agree", "Agree", "Neutral", "Disagree","Strongly_Disagree"))
  
  new.d <- data.frame(new.d, c2a3)
  new.d <- apply_labels(new.d, c2a3 = "Safe in Neighborhood: Childhood or young adult life")
  
  print("Childhood or young adult life")
  summary(new.d$c2a3)
}
```

# C4
C4. Thinking about your NEIGHBORS, as a whole, during the following 3 time periods:	
a. How often do/did you see neighbors talking outside in the yard, on the street, at the corner park, etc.?	
1=Often  
2=Sometimes  
3=Rarely/Never
88=Don’t Know
```{r C4: neighbors talking outside }
print("Neighbors talking outside")
if("c4a1" %in% varName.list) { 
  c4a1 <- as.factor(d[,"c4a1"])  # * gets treated as NA by not including it in levels
  levels(c4a1) <- list(Often="1",
                     Sometimes="2",
                     Rarely_Never="3",
                     Do_Not_Know="88")
  
  new.d <- data.frame(new.d, c4a1)
  new.d <- apply_labels(new.d, c4a1 = "Neighbors talking outside: Current")
  
  print("Current")
  summary(new.d$c4a1)
}

if("c4a2" %in% varName.list) { 
  c4a2 <- as.factor(d[,"c4a2"])  # * gets treated as NA by not including it in levels
  levels(c4a2) <- list(Often="1",
                     Sometimes="2",
                     Rarely_Never="3",
                     Do_Not_Know="88")
  
  new.d <- data.frame(new.d, c4a2)
  new.d <- apply_labels(new.d, c4a2 = "Neighbors talking outside: Age 31 up to just before prostate cancer diagnosis")
  
  print("Age 31 up to just before prostate cancer diagnosis")
  summary(new.d$c4a2)
}

if("c4a3" %in% varName.list) { 
  c4a3 <- as.factor(d[,"c4a3"])  # * gets treated as NA by not including it in levels
  levels(c4a3) <- list(Often="1",
                     Sometimes="2",
                     Rarely_Never="3",
                     Do_Not_Know="88")
  
  new.d <- data.frame(new.d, c4a3)
  new.d <- apply_labels(new.d, c4a3 = "Neighbors talking outside: Childhood or young adult life")
  
  print("Childhood or young adult life")
  summary(new.d$c4a3)
}

```

# D1
D1. In the following questions, we are interested in your perceptions about the way other people have treated you because of your race/ethnicity or skin color.
```{r Treatment becasue of race/ethnicity or skin color }
if("d1aa" %in% varName.list) { 
  d1aa <- ifelse(d[, "d1aa"]=="*", NA, ifelse(d[, "d1aa"]=="NA", NA, d[, "d1aa"]))
  d1aa  <- as.factor(d1aa)
  levels(d1aa) <- list(No="1",Yes="2")
  
  new.d <- data.frame(new.d, d1aa)
  new.d <- apply_labels(new.d, d1aa = "Have you ever been unfairly fired from a job or been unfairly denied a promotion?")
  
  print("Denied a promotion")
  summary(new.d$d1aa)
}

if("d1ab" %in% varName.list) { 
  d1ab <- ifelse(d[, "d1ab"]=="*", NA, ifelse(d[, "d1ab"]=="NA", NA, d[, "d1ab"]))
  d1ab  <- as.factor(d1ab)
  levels(d1ab) <- list(Not_at_all="1",A_little="2", Somewhat="3",Extremely="4")
  
  new.d <- data.frame(new.d, d1ab)
  new.d <- apply_labels(new.d, d1ab = "If yes, How stressful was this experience?")
  
  print("Stress from denied a promotion")
  summary(new.d$d1ab)
}

if("d1ba" %in% varName.list) { 
  d1ba <- ifelse(d[, "d1ba"]=="*", NA, ifelse(d[, "d1ba"]=="NA", NA, d[, "d1ba"]))
  d1ba  <- as.factor(d1ba)
  levels(d1ba) <- list(No="1",Yes="2")
  
  new.d <- data.frame(new.d, d1ba)
  new.d <- apply_labels(new.d, d1ba = "For unfair reasons, have you ever not been hired for a job?")
  
  print("Not hired for a job")
  summary(new.d$d1ba)
}

if("d1bb" %in% varName.list) { 
  d1bb <- ifelse(d[, "d1bb"]=="*", NA, ifelse(d[, "d1bb"]=="NA", NA, d[, "d1bb"]))
  d1bb  <- as.factor(d1bb)
  levels(d1bb) <- list(Not_at_all="1",A_little="2", Somewhat="3",Extremely="4")
  
  new.d <- data.frame(new.d, d1bb)
  new.d <- apply_labels(new.d, d1ab = "If yes, How stressful was this experience?")
  
  print("Stress from not hired for a job")
  summary(new.d$d1bb)
}

if("d1ca" %in% varName.list) { 
  d1ca <- ifelse(d[, "d1ca"]=="*", NA, ifelse(d[, "d1ca"]=="NA", NA, d[, "d1ca"]))
  d1ca  <- as.factor(d1ca)
  levels(d1ca) <- list(No="1",Yes="2")
  
  new.d <- data.frame(new.d, d1ca)
  new.d <- apply_labels(new.d, d1ca = "Have you ever been unfairly stopped, searched, questioned, physically threatened or abused by the police?")
  
  print("Unfair police")
  summary(new.d$d1ca)
}

if("d1cb" %in% varName.list) { 
  d1cb <- ifelse(d[, "d1cb"]=="*", NA, ifelse(d[, "d1cb"]=="NA", NA, d[, "d1cb"]))
  d1cb  <- as.factor(d1cb)
  levels(d1cb) <- list(Not_at_all="1",A_little="2", Somewhat="3",Extremely="4")
  
  new.d <- data.frame(new.d, d1cb)
  new.d <- apply_labels(new.d, d1cb = "If yes, How stressful was this experience?")
  
  print("Stress from unfair police")
  summary(new.d$d1cb)
}

if("d1da" %in% varName.list) { 
  d1da <- ifelse(d[, "d1da"]=="*", NA, ifelse(d[, "d1da"]=="NA", NA, d[, "d1da"]))
  d1da  <- as.factor(d1da)
  levels(d1da) <- list(No="1",Yes="2")
  
  new.d <- data.frame(new.d, d1da)
  new.d <- apply_labels(new.d, d1da = "Have you ever been unfairly discouraged by a teacher or advisor from continuing your education?")
  
  print("Unfair education")
  summary(new.d$d1da)
}

if("d1db" %in% varName.list) { 
  d1db <- ifelse(d[, "d1db"]=="*", NA, ifelse(d[, "d1db"]=="NA", NA, d[, "d1db"]))
  d1db  <- as.factor(d1db)
  levels(d1db) <- list(Not_at_all="1",A_little="2", Somewhat="3",Extremely="4")
  
  new.d <- data.frame(new.d, d1db)
  new.d <- apply_labels(new.d, d1db = "If yes, How stressful was this experience?")
  
  print("Stress from unfair education")
  summary(new.d$d1db)
}

if("d1ea" %in% varName.list) { 
  d1ea <- ifelse(d[, "d1ea"]=="*", NA, ifelse(d[, "d1ea"]=="NA", NA, d[, "d1ea"]))
  d1ea  <- as.factor(d1ea)
  levels(d1ea) <- list(No="1",Yes="2")
  
  new.d <- data.frame(new.d, d1ea)
  new.d <- apply_labels(new.d, d1ea = "Have you ever been unfairly prevented from moving into a neighborhood because the landlord or a realtor refused to sell or rent you a house or apartment?")
  
  print("Unfair neighborhood")
  summary(new.d$d1ea)
}

if("d1eb" %in% varName.list) { 
  d1eb <- ifelse(d[, "d1eb"]=="*", NA, ifelse(d[, "d1eb"]=="NA", NA, d[, "d1eb"]))
  d1eb  <- as.factor(d1eb)
  levels(d1eb) <- list(Not_at_all="1",A_little="2", Somewhat="3",Extremely="4")
  
  new.d <- data.frame(new.d, d1eb)
  new.d <- apply_labels(new.d, d1eb = "If yes, How stressful was this experience?")
  
  print("Stress from unfair neighborhood")
  summary(new.d$d1eb)
}

if("d1fa" %in% varName.list) { 
  d1fa <- ifelse(d[, "d1fa"]=="*", NA, ifelse(d[, "d1fa"]=="NA", NA, d[, "d1fa"]))
  d1fa  <- as.factor(d1fa)
  levels(d1fa) <- list(No="1",Yes="2")
  
  new.d <- data.frame(new.d, d1fa)
  new.d <- apply_labels(new.d, d1fa = "Have   you   ever   been   unfairly denied a bank loan?")
  
  print("Unfairly denied bank loan")
  summary(new.d$d1fa)
}

if("d1fb" %in% varName.list) { 
  d1fb <- ifelse(d[, "d1fb"]=="*", NA, ifelse(d[, "d1fb"]=="NA", NA, d[, "d1fb"]))
  d1fb  <- as.factor(d1fb)
  levels(d1fb) <- list(Not_at_all="1",A_little="2", Somewhat="3",Extremely="4")
  
  new.d <- data.frame(new.d, d1fb)
  new.d <- apply_labels(new.d, d1fb = "If yes, How stressful was this experience?")
  
  print("Stress from nfairly denied bank loan")
  summary(new.d$d1fb)
}

if("d1ga" %in% varName.list) { 
  d1ga <- ifelse(d[, "d1ga"]=="*", NA, ifelse(d[, "d1ga"]=="NA", NA, d[, "d1ga"]))
  d1ga  <- as.factor(d1ga)
  levels(d1ga) <- list(No="1",Yes="2")
  
  new.d <- data.frame(new.d, d1ga)
  new.d <- apply_labels(new.d, d1ga = "Have   you   ever   been   unfairly treated when getting medical care?")
  
  print("Unfair medical care")
  summary(new.d$d1ga)
}

if("d1gb" %in% varName.list) { 
  d1gb <- ifelse(d[, "d1gb"]=="*", NA, ifelse(d[, "d1gb"]=="NA", NA, d[, "d1gb"]))
  d1gb  <- as.factor(d1gb)
  levels(d1gb) <- list(Not_at_all="1",A_little="2", Somewhat="3",Extremely="4")
  
  new.d <- data.frame(new.d, d1gb)
  new.d <- apply_labels(new.d, d1gb = "If yes, How stressful was this experience?")
  
  print("Stress from unfair medical care")
  summary(new.d$d1gb)
}

```

#D3B
b. You have received poorer service than other people at restaurants or stores
```{r Received poorer service }
if("d3b1" %in% varName.list) { 
  d3b1 <- ifelse(d[, "d3b1"]=="*", NA, ifelse(d[, "d3b1"]=="NA", NA, d[, "d3b1"]))
  d3b1  <- as.factor(d3b1)
  levels(d3b1) <- list(Never="1",Rarely="2", Sometimes="3",Often="4")

  new.d <- data.frame(new.d, d3b1)
  new.d <- apply_labels(new.d, d3b1 = "Current (from prostate cancer diagnosis to the present)")
  
  print("Current")
  summary(new.d$d3b1)
}

if("d3b2" %in% varName.list) { 
  d3b2 <- ifelse(d[, "d3b2"]=="*", NA, ifelse(d[, "d3b2"]=="NA", NA, d[, "d3b2"]))
  d3b2  <- as.factor(d3b2)
  levels(d3b2) <- list(Never="1",Rarely="2", Sometimes="3",Often="4")

  new.d <- data.frame(new.d, d3b2)
  new.d <- apply_labels(new.d, d3b2 = " Age 31 up to just before prostate cancer diagnosis")
  
  print("Before prostate cancer diagnosis")
  summary(new.d$d3b2)
}

if("d3b3" %in% varName.list) { 
  d3b3 <- ifelse(d[, "d3b3"]=="*", NA, ifelse(d[, "d3b3"]=="NA", NA, d[, "d3b3"]))
  d3b3  <- as.factor(d3b3)
  levels(d3b3) <- list(Never="1",Rarely="2", Sometimes="3",Often="4")

  new.d <- data.frame(new.d, d3b3)
  new.d <- apply_labels(new.d, d3b3 = "Childhood or young adult life (up to age 30)")
  
  print("Childhood and young adult")
  summary(new.d$d3b3)
}

```

# D4
D4. These statements are about how you currently see yourself. Indicate your level of agreement or disagreement with each statement.
```{r Currently see yourself }
tmp.d <- data.frame(matrix(ncol=0, nrow=nrow(new.d)))
for(i in letters[1:12]) {
  q.term <- paste("d4", i, sep="")
  q.v <- ifelse(d[, q.term]=="*", NA, ifelse(d[, q.term]=="NA", NA, d[, q.term]))
  q.v  <- as.factor(q.v)
  levels(q.v) <- list(Strongly_Agree="1",Somewhat_Agree="2", Somewhat_Disagree="3",Strongly_Disagree="4")
  tmp.d <- data.frame(tmp.d, q.v)
  label <- switch(i, "a" = "a. You’ve always felt that you could make of your life pretty much what you wanted to make of it.",
                      "b" = "b. Once you make up your mind to do something, you stay with it until the job is completely done.",
                      "c" = "c. You like doing things that other people thought could not be done.",
                      "d" = "d. When things don’t go the way you want them to, that just makes you work even harder.",
                      "e" = "e. Sometimes, you feel that if anything is going to be done right, you have to do it yourself.",
                      "f" = "f. It’s not always easy, but you manage to find a way to do the things you really need to get done.",
                      "g" = "g. Very seldom have you been disappointed by the results of your hard work.",
                      "h" = "h. You feel you are the kind of individual who stands up for what he believes in, regardless of the consequences.",
                      "i" = "i. In the past, even when things got really tough, you never lost sight of your goals.",
                      "j" = "j. It’s important for you to be able to do things the way you want to do them rather than the way other people want you to do them.",
                      "k" = "k. You don’t let your personal feelings get in the way of doing a job.",
                      "l" = "l. Hard work has really helped you to get ahead in life.")
  tmp.d <- apply_labels(tmp.d, q.v = label)
  names(tmp.d)[names(tmp.d)=="q.v"] <- q.term
  
  #print(label)
  #print(summary(new.d[,q.term]))
}
summarytools::view(dfSummary(tmp.d, style = 'grid', max.distinct.values = 100), method="render", report.title="All Data")
  lapply(unique(new.d$locationname), FUN=function(loc) { summarytools::view(dfSummary(tmp.d[new.d$locationname==loc,], style = 'grid', max.distinct.values = 100), method="render", report.title = as.character(loc))})
  #summary(new.d$locationname)
  new.d <- data.frame(new.d, tmp.d)
  rm(tmp.d)

```

# D5
D5. The next questions are about the time period of your childhood, before the age of 18. These are standard questions asked in many surveys of life history. This information will allow us to understand how problems that may occur early in life may affect health later in life. This is a sensitive topic and some people may feel uncomfortable with these questions. Please keep in mind that you can skip any question you do not want to answer. All information is kept confidential.
When you were growing up, during the first 18 years of your life…
```{r Childhood questions }
for(i in letters[1:4]) {
  q.term <- paste("d5", i, sep="")
  q.v <- ifelse(d[, q.term]=="*", NA, ifelse(d[, q.term]=="NA", NA, d[, q.term]))
  q.v  <- as.factor(q.v)
  levels(q.v) <- list(No="1",Yes="2", Do_Not_Know="88",Prefer_Not_to_Answer="99")
  new.d <- data.frame(new.d, q.v)
  label <- switch(i, "a" = "a. Did you live with anyone who was depressed, mentally ill, or suicidal?",
                      "b" = "b. Did you live with anyone who was a problem drinker or alcoholic?",
                      "c" = "c. Did you live with anyone who used illegal street drugs or who abused prescription medications?",
                      "d" = "d. Did you live with anyone who served time or was sentenced to serve time in a prison, jail, or other correctional facility?")
  new.d <- apply_labels(new.d, q.v = label)
  names(new.d)[names(new.d)=="q.v"] <- q.term
  
  print(label)
  print(summary(new.d[,q.term]))
}

i <- "e"
q.term <- paste("d5", i, sep="")
q.v <- ifelse(d[, q.term]=="*", NA, ifelse(d[, q.term]=="NA", NA, d[, q.term]))
q.v  <- as.factor(q.v)
levels(q.v) <- list(No="1",Yes="2", Parents_not_married="3", Do_Not_Know="88",Prefer_Not_to_Answer="99")
new.d <- data.frame(new.d, q.v)
label <- switch(i, "e" = "e. Were your parents separated or divorced?")
new.d <- apply_labels(new.d, q.v = label)
names(new.d)[names(new.d)=="q.v"] <- q.term

print(label)
print(summary(new.d[,q.term]))
  
for(i in letters[6:11]) {
  q.term <- paste("d5", i, sep="")
  q.v <- ifelse(d[, q.term]=="*", NA, ifelse(d[, q.term]=="NA", NA, d[, q.term]))
  q.v  <- as.factor(q.v)
  levels(q.v) <- list(Never="1",Once="2", More_than_once="3", Do_Not_Know="88",Prefer_Not_to_Answer="99")
  
  new.d <- data.frame(new.d, q.v)
  label <- switch(i, "f" = "f. How often did your parents or adults in your home ever slap, hit, kick, punch or beat each other up?",
                      "g" = "g. How often did a parent or adult in your home ever hit, beat, kick, or physically hurt you in any way? Do not include spanking.",
                      "h" = "h. How often did a parent or adult in your home ever swear at you, insult you, or put you down?",
                      "i" = "i. How often did anyone at least 5 years older than you or an adult, ever touch you sexually?",
                      "j" = "j. How often did anyone at least 5 years older than you or an adult, try to make you touch them sexually?",
                      "k" = "k. How often did anyone at least 5 years older than you or an adult, force you to have sex?")
  new.d <- apply_labels(new.d, q.v = label)
  names(new.d)[names(new.d)=="q.v"] <- q.term
  
  print(label)
  print(summary(new.d[,q.term]))
}

```



# Final Summary
```{r final summary }

summarytools::view(dfSummary(new.d, style = 'grid', max.distinct.values = 100), method="browser", report.title="All Data")
lapply(unique(new.d$locationname), FUN=function(loc) { summarytools::view(dfSummary(new.d[new.d$locationname==loc,], style = 'grid', max.distinct.values = 100), method="browser", report.title = as.character(loc))})
```

