---
title: "Merge Registry and JHU Data"
author: "RESPOND Core D Team"
date: "`r format(Sys.time(), '%Y-%m-%d')`"
output:
  html_document:
    toc: true
    toc_float: true
    df_print: paged
    code_folding: hide
  pdf_document: default
---

```{r setup, include=FALSE}
require("RPostgreSQL") # for PostgreSQL
library(zoo) # for date conversion
library(expss) # for labels
library(DBI) # for Database connectivity
library(summarytools) # for summarizing variables
library(tidyverse)
library(plyr)
library(knitr) # for creating tables
#library(questionr)
library(table1)
library(xtable)
library(ggplot2)
#library(epiDisplay)
library(memisc)

knitr::opts_chunk$set(warning = FALSE)

```

```{r input data} 
# set working directory
setwd("/Volumes/GoogleDrive/My Drive/Projects/RESPOND/CORE D/DataProcessingCleaningCreation/TumorMerge/")
available_data_files <- list.files("../Data/")
available_database_files <- list.files("../Data/DataFromDatabase/")
load(paste("../Data/", sort(available_data_files[grep("vsurvall_analysis_", available_data_files)], decreasing = T)[1], sep=""))
load(paste("../Data/DataFromDatabase/", sort(available_database_files[grep("vjhusamples", available_database_files)], decreasing = T)[1], sep=""))
load(paste("../Data/", sort(available_data_files[grep("vregall_analysis_", available_data_files)], decreasing = T)[1], sep=""))

d <- merge(x=d, y=disease_characteristics, by.x="respondid", by.y="d.respondid", all.x=TRUE, all.y=TRUE)
d <- merge(x=d, y=vjhusamples, by.x="respondid", by.y="respondid", all.x=FALSE, all.y=FALSE)



```

# Description

This report is merges the registry data and the survey data in the RESPOND study.

### Total Number of Individuals: `r nrow(d)`

# REGISTRY	
```{r registry }  
registry_count <- d %>% 
  group_by(registry) %>% 
  dplyr::summarise(n = n())
kable(registry_count, format = "simple", align = 'l', caption = "Overview of all registries")
```


# RESPOND ID
* From Barcode label put on last page of survey by registries, identifies participant. RESPOND_ID is assigned by the registries.
```{r respond id, echo=FALSE}
d_respondid <- filter(d, !is.na(respondid))

isDup_respondid <- duplicated(d_respondid$respondid)
numDups_respondid <- sum(isDup_respondid)
dups_respondid <- d_respondid[isDup_respondid, 'respondid']

```

    + Number of duplicates: `r numDups_respondid`
    + The following are duplicated IDs:
    + `r dups_respondid`

    + Number of NAs: `r sum(is.na(d$respondid))`


# SURVEY ID
- Scantron assigned SurveyID
```{r survey ID, echo=FALSE}
isDup_surveyid <- duplicated(d$surveyid)
numDups_surveyid <- sum(isDup_surveyid)
dups_surveyid <- d[isDup_surveyid, 'surveyid']

```


    + Number of duplicates: `r numDups_surveyid`
    + The following are duplicated IDs:
    + `r dups_surveyid`


    + Number of NAs: `r sum(is.na(d$surveyid))`


```{r create_Rda_data, echo=FALSE}
save(d, file=paste("../Data/vjhu_", format(Sys.time(), "%Y%m%d"), ".Rda", sep=""))
write.table(d, file=paste("../Data/vjhu_", format(Sys.time(), "%Y%m%d"), ".csv", sep=""), sep=",", quote=F, row.names=F)
```

