---
title: "Survey Cleaning"
author: "RESPOND Core D Team"
date: "`r format(Sys.time(), '%Y-%m-%d')`"
output:
  html_document:
    toc: true
    toc_float: true
    df_print: paged
    code_folding: hide
  pdf_document: default

---

```{r setup, include=FALSE}
require("RPostgreSQL") # for PostgreSQL
library(zoo) # for date conversion
#library(expss) # for labels
library(DBI) # for Database connectivity
library(summarytools) # for summarizing variables
library(gtsummary)
library(tidyverse)
library(plyr)
library(dplyr)
library(knitr) # for creating tables
library(questionr)
library(kableExtra)
library(readxl)
```

```{r input survey data, include=FALSE} 

setwd("/Volumes/GoogleDrive/My Drive/Projects/RESPOND/CORE D/DataProcessingCleaningCreation/Survey")
available_data_files <- list.files("../Data/DataFromDatabase/")
load(paste("../Data/DataFromDatabase/", available_data_files[grep("vsurvall", available_data_files)], sep=""))
load(paste("../Data/DataFromDatabase/", available_data_files[grep("vsiteid", available_data_files)], sep=""))

# remove spaces for now
vsiteid <- vsiteid %>% 
  mutate(registrywid = gsub(" ", "_", registrywid))

# working data.frame, with some cleaning of IDs etc
d <- vsurvall %>% 
  left_join(vsiteid, 'siteid') %>% 
  # trim whitespace from surveyid
  mutate(surveyid = trimws(surveyid))

# input the variable information including variable name (<var>), label for table of contents and headings (<title>), item description or question asked on survey (<item>), and variable values (<response>)
variable_information <- read_xlsx("Survey Data Dictionary/SurveyVariablesInformationRPMOD_final20220312.xlsx")
#variable_information <- variable_information[40:60,]  #shorter list for testing...
variables <- variable_information$var

```


<!-- read script containing useful code -->
```{r child = 'Survey_Cleaning_Chunks.Rmd', echo = F}
```

# Overall Report Description

This report is step two of a three step process for data organization in the RESPOND study.

## Data Processing, Cleaning, and Creation Description
```{r child="Survey_Description.Rmd" }
```

```{r clean survey data, echo=FALSE}
source("Survey_Cleaning_Functions.R")

d <- run_survey_cleaning(dat=d, variables=variables)

```

## Total number of records: `r nrow(d)`

# REGISTRY	
```{r registry }  
registry_count <- d %>% 
  group_by(registry) %>% 
  dplyr::summarise(n = n())
kable(registry_count, format = "simple", align = 'l', caption = "Overview of all registries")
```


# RESPOND ID
* From Barcode label put on last page of survey by registries, identifies participant. RESPOND_ID is assigned by the registries.
```{r respond id, echo=FALSE}
d_respondid <- filter(d, !is.na(respondid))

isDup_respondid <- duplicated(d_respondid$respondid)
numDups_respondid <- sum(isDup_respondid)
dups_respondid <- d_respondid[isDup_respondid, 'respondid']

```

    + Number of duplicates: `r numDups_respondid`
    + The following are duplicated IDs:
    + `r dups_respondid`

    + Number of NAs: `r sum(is.na(d$respondid))`


# SURVEY ID
- Scantron assigned SurveyID
```{r survey ID, echo=FALSE}
isDup_surveyid <- duplicated(d$surveyid)
numDups_surveyid <- sum(isDup_surveyid)
dups_surveyid <- d[isDup_surveyid, 'surveyid']

```


    + Number of duplicates: `r numDups_surveyid`
    + The following are duplicated IDs:
    + `r dups_surveyid`


    + Number of NAs: `r sum(is.na(d$surveyid))`


```{r summary_survey_variables, results = 'asis'}
# function to report frequency table by variable looped over sites
tab_var <- function(dat, var, variable_information) {
  <<freq_table>>
}

# walk over VARIABLES
walk(variables, ~ tab_var(dat = d, var = .x, variable_information = variable_information))
```

```{r create_Rda_data, echo=FALSE}
save(d, file=paste("../Data/vsurvall_cleaned_", format(Sys.time(), "%Y%m%d"), ".Rda", sep=""))

```
